---
title: "rnd"
author: "Liz Miller"
date: "6/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```

## RnD Analysis: IC_CENTER, PROJECT_NUMBER, PROJECT_TITLE, PROJECT_TERMS

Preliminary analysis for RnD project.

Taking the subset of the data for analysis:

```{r subsetting the data, message=FALSE, warning=FALSE}
library(tidyverse)
library(tidytext)

raw_abstracts <- read.csv('/project/biocomplexity/sdad/projects_data/ncses/prd/RND_Topic_Modelling/Raw_Data/raw_abstracts.csv')

data_subset <- raw_abstracts %>%
  select(IC_CENTER, PROJECT_NUMBER, PROJECT_TITLE, PROJECT_TERMS)

data_subset <- data_subset %>% mutate_all(na_if,"")
```

## Analysis for Project_Number and Project_Terms
I decided to focus on the project title and the project terms, as the project number didn't seem particularly meaningful. I used the Text Mining with R (tidytextmining.com) to look at the frequency and weights of the words in both the title and the terms by IC center. 

```{r process for turning the text into a tidy format, message=FALSE, warning=FALSE}
#Tidying the data

project_terms <- data_subset %>%
  select(IC_CENTER, PROJECT_TERMS)
project_titles <- data_subset %>%
  select(IC_CENTER, PROJECT_TITLE)

tidy_terms <- tibble(ic = project_terms$IC_CENTER, text = project_terms$PROJECT_TERMS)
tidy_titles <- tibble(ic = project_titles$IC_CENTER, 
                      text = project_titles$PROJECT_TITLE)

tidy_terms <- tidy_terms %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words) %>%
  count(ic, word, sort = TRUE)
tidy_titles <- tidy_titles %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words) %>%
  count(ic, word, sort = TRUE)
```
##Word Frequencies

```{r word frequency ggplots, message=FALSE, warning=FALSE, paged.print=TRUE}

tidy_terms %>%
  count(word, sort = TRUE) %>%
  filter(n > 200000) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  ggtitle("Terms")

tidy_titles %>%
  count(word, sort = TRUE) %>%
  filter(n > 10000) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() +
  ggtitle("Titles")
```
##Deeper Analysis Using tf-idf

Words are weighted based upon their frequency and exclusivity in each IC category. 

```{r task, message=FALSE, warning=FALSE}
#if-idf
total_terms <- tidy_terms %>%
  group_by(ic) %>%
  summarize(total = sum(n))

total_titles <- tidy_titles %>%
  group_by(ic) %>%
  summarize(total = sum(n))

tidy_terms <- left_join(tidy_terms, total_terms)
tidy_titles <- left_join(tidy_titles, total_titles)

tidy_terms <- tidy_terms %>%
  bind_tf_idf(word, ic, n)

tidy_titles <- tidy_titles %>%
  bind_tf_idf(word, ic, n)
```
#Words Highly Cooralated by IC

```{r important words by IC, message=FALSE, warning=FALSE}

#Function for easily creating graphs
important_words <- function(df, agency) {
  selected <- df %>% filter(ic == agency)
  selected %>%
    arrange(desc(tf_idf)) %>%
    mutate(word = factor(word, levels = rev(unique(word)))) %>%
    group_by(ic) %>%
    top_n(10) %>%
    ungroup() %>%
    ggplot(aes(word, tf_idf, fill = ic)) +
    geom_col(show.legend = FALSE) +
    labs(x = NULL, y = "tf_idf") +
    facet_wrap(~ic, ncol = 2, scales = "free") +
    coord_flip()
} 
important_words(tidy_terms, c("FDA", "VA", "CDC", "NIAID"))
important_words(tidy_titles, c("FDA", "VA", "CDC", "NIAID"))

```
#Doing the same steps as above for the abstracts data
or at least, that's the plan, let's see how far we get 

```{r abstracts analysis, message=FALSE, warning=FALSE}
abstracts <- raw_abstracts %>%
    select(IC_CENTER, ABSTRACT)

tidy_abstracts <- tibble(ic = abstracts$IC_CENTER, text = abstracts$ABSTRACT)

tidy_abstracts <- tidy_abstracts %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words) %>%
  count(ic, word, sort = TRUE)

tidy_abstracts %>%
  count(word, sort = TRUE) %>%
  filter(n > 500000) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(word, n)) +
  geom_col() +
  xlab(NULL) +
  coord_flip() 

total_abstracts <- tidy_abstracts %>%
group_by(ic) %>%
summarize(total = sum(n))

tidy_abstracts <- left_join(tidy_abstracts, total_abstracts)

tidy_abstracts <- tidy_abstracts %>%
bind_tf_idf(word, ic, n)

important_words(tidy_abstracts, c("FDA", "VA", "CDC", "NIAID"))
 
